\section{Experiment}

\subsection{Data Description and Experimental Protocol}

In this section, we introduce seven experimented data sets 
and experimental protocols.

Three data sets are security related. One is the Spam Email 
data set downloaded from the UCI data repository; 
it contains 4601 profiled emails categorized into spam emails 
and normal emails. Another one is the Big Malware 
classification Challenge 2015 data set downloaded 
from Kaggle 
\footnote{https://www.kaggle.com/c/malware-classification}; 
it contains approximately 10,000 profiled malware files that 
are categorized into nine families, including Ramnit, 
Lollipop, Vundo, etc. The third one is the Coburg Intrusion Detection data set recently created by Ring et al. 
\cite{ring2017flow}; it contains approximately 
32 million profiled network flows collected in a 
period of 4 weeks and categorized into five classes, 
namely, attack, normal, suspicious, unknown and victim. 

The other four data sets are widely used for anomaly 
detection task, and are downloaded from Stony Brook 
University's Outlier Detection DataSets\footnote{http://odds.cs.stonybrook.edu/}. 
One is the Satellite data set; it contains 6435 
profiled patches of satellite images that are divided 
into 36 different classes, including red soil, cotton crop, 
grey soil,etc. Another one is the Ionosphere data set; 
it contains 351 profiled radar-transmitted signals that 
are classified into anomalous and normal signals. 
The third one is the Cardio data set; it contains 1831 
profiled patients classified into anomalous, suspect and 
normal patients. The last one is Arrhythmia data set; 
it contains 452 profiled patients with or without the 
presence of cardiac arrhythmia. 

To examine predictive demographic disparity, we 
collected the Crime Community data set \cite{redmond2002data}. 
It contains 1994 profiled U.S. communities 
labeled by their recorded violent crime rates. 
We binarized crime rates such that those above 50\% (high-risk 
communities) were encoded as 1, and those below 50\% (low-risk communities) were encoded as -1. 

All categorical features were encoded by dummy variables. 

In each experiment, we randomly chose 50\% instances on 
a data set for training and used the rest for testing. 
We repeated the random trials for 20 times, and reported 
the averaged prediction qualities. Hyper-parameters of 
all models were optimized through grid search, 
and those yielding optimal testing performance were selected. 

